### 2012-12-07 doc/description.tex
orm exmplained

\begin{verbatim}
Application = < Class*, Instance*>
\end{verbatim}
The application is considered to be consistent if all instances are created according a class existing in the application.

@@

\newpage
\appendix
\section{Object-Relational Mapping}
There are defined functions for object-relational mapping used in the model. The purpose of a function is indicated in its name and should be obvious from its definition.

@@

\subsection{Mapping of Associations}
\begin{verbatim}

\end{verbatim}

>>>>

\begin{verbatim}
op application : List{Class} List{Instance} -> Application [ctor] .
\end{verbatim}
The application is considered to be consistent if all instances are created according a class existing in the application.

@@

\section{Database model}
The relational database consists of database schema which defines the structure of the database and data. The database is a pair od sets:
\begin{verbatim}
op database : List{Table} List{Row} -> Database [ctor] .
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\appendix
\section{Object-Relational Mapping}
There are defined functions for object-relational mapping used in the model. The purpose of a function is indicated in its name and should be obvious from its definition.

@@

\subsection{Mapping of Associations}
A association is mapped into database as a foreign key in table representing associating class or an association can be mapped as a coupling table in case the association cardinality is M:N or 1:N . 
\begin{verbatim}
op associations2db : Qid List{Association} Database -> Database .
op associations2db : Qid Association Database -> Database .

eq associations2db(Q, [], D) = D .
eq associations2db(Q, Assoc, EDb) = EDb .
ceq associations2db(Q, Assoc, D) = addFK(foreignKey(name(Assoc), Q, NOTNULL), 
	   referenceA(Assoc), D) if startCardinality(Assoc) < 2 . 
eq associations2db(Q, Assoc, D) = addTable(table(name(Assoc), 
   primaryKey('Id'), [], 
   foreignKey(Q, Q, NOTNULL) 
   foreignKey(name(Assoc), name(Assoc), NOTNULL)), D) .
	eq associations2db(Q, Assoc, D) = associations2db(Q, tail(Assoc), 
   associations2db(Q, head(Assoc), D)) .
\end{verbatim}
